\cvsection{Research Projects}

\begin{cventries}

  \cventry
    {NCSU, advised by Dongkuan Xu, Xipeng shen} % Empty position
    {Zero-shot Code Generation via Rule-AI Co-learning from Document} % Project
    {} % Empty location
    {Aug. 2022 - } % Empty date
    { 
     \begin{cvitems} % Description(s) bullet points
       \item{Designed a zero-shot code generation framework to generate DSL code from document knowledge.}
       \item{Used retriever to get APIs related to query, let rule-based method generate code based on them.}
       \item{Trained CodeT5 on data generated from rule-based method.}
       \item{Update the retriever with the encoder section of CodeT5 to better retrieve relevant document information for queries.}
     \end{cvitems}
    }

 \vspace{0mm} 


  \cventry
{Temple University, advised by Wenpeng Yin} % Empty position
{Robustness of learning from task instructions} % Project
{} % Empty location
{May. 2022 - Jul. 2022} % Empty date
{ 
	     \begin{cvitems} % Description(s) bullet points
		       \item{Verified and analyzed the robustness of Tk-instruct on natural instruction v2 dataset.}
		       \item{Tampered instructions and created new different version to check the robustness in evaluation.}
		       \item{Prepend multiple-version instruction and add adversarial attack to improve robustness.}
		     \end{cvitems}
}

 \vspace{0mm} 
 
  \cventry
{USC, advised by Pedro Szekely} % Empty position
{Integrating factual information of language models into knowledge graph embeddings} % Project
{} % Empty location
{Jan. 2022 - May. 2022} % Empty date
{ 
	     \begin{cvitems} % Description(s) bullet points
		       \item{Use prompts to mine factual information from language models to complete downstream tasks.}
		       \item{Trained RotatE link prediction models on YAGO3-10 dataset.}
		       \item{Using KnowBERT, GPT-Neo as the evaluation model to calculate perplexity of sentences constructed from triples.}
                  \item{Adjust the scores of link predictions by perplexity, hits@1, hits@5 improved by 20\%.}
		     \end{cvitems}
}


 
 \vspace{0mm} 

\end{cventries}
